PM Mungbean meta-analysis

### 2021-01-29 02_Preliminary_analysis.Rmd
Edits mainly spelling and grammar

All fungicide ai treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.

@@

Lets look at how many trials were undertaken each season in trials including DMI fungicides.

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
   table(tmp1$year)
```

@@

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha. * 1000),
             maximum_yield = max(grain_yield.t.ha. * 1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_SE = sd(grain_yield.t.ha. * 1000)/
                              sqrt(n())) %>%
   kable(align = 'c',
   caption = "Average yield statistics for no spray contol plots"
)

@@

What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
```{r ControlYield_DMITrials}
DMITrials <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref)%>%
   pull()

PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%
   filter(fungicide_ai == "control" )%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for control plots in trials which used a DMI fungicide")

@@

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

Lets look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.

```{r Calculate_yield-savings}
for (i in unique(PM_MB_dat$trial_ref)) {
   # Loop code over each trial reference
   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i, ]

@@

   for (j in unique(dat1$row_spacing)) {
      # Loop within trial row_spacing
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps

@@

      # Reassign values to row_spacing subset
      dat1[dat1$row_spacing == j, ] <- dat2
   }
   # Reassign values to trial_ref subset
   PM_MB_dat[PM_MB_dat$trial_ref == i, ] <- dat1
}

# ____________________________________________
# calculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ]

@@

PM_MB_dat[PM_MB_dat$trial_ref == "AM1303", ] <- dat1
```

Lets show the yield gains in each trial as a table and plot
```{r YieldGain_table}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   group_by(trial_ref, location, year)%>%
   summarise(yield_gain_m = mean(yield_gain),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             yg_n = n(),
             .groups = "drop")%>%
   arrange(yield_gain_m)
```

```{r Yield_plot}

bw_labels <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>% 
   group_by(trial_ref, location, year)%>%
   summarise(m_gy = mean(grain_yield.t.ha.)) %>%
   mutate(trial = paste(location,year,sep = "\n")) %>%
   arrange(m_gy) %>%
   pull(trial)

bw_labels[1] <- paste0(bw_labels[1],"(b)")
bw_labels[3] <- paste0(bw_labels[3],"(a)")

fungicide_spray_plot <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "Fungicide treated"))%>%
   group_by(trial_ref, location, year)%>%
   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., fill = spray_treat))+
   geom_boxplot()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   xlab("Trial location and year")+
   ylab(bquote('Mungbean yield  '*t~ha^-1*''))+
   scale_x_discrete(labels = bw_labels)+
   ylim(0,2.5)+
   scale_fill_grey(start = 1, end = 0.7)+
   labs(colour = "Fungicide treatment")+
   guides(fill = guide_legend(title = "Treatment"))

@@

Lets inspect a summary of both powdery mildew severity and grain yield for trials including DMI funcgicides.

```{r Full_Trial_Summary_table, warning= FALSE}
Sev_yield_table <-
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(trial_ref = str_remove(trial_ref, "mung"))%>%  # remove "mung" prefix from trial_ref
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE),digits = 2),
             n_controls = sum(is.na(PM_sev_control) == FALSE),
             min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE),digits = 2),
             max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE),digits = 2),
             m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE),digits = 3),
             min_PM_yield = round(min(PM_y_treat, na.rm = TRUE),digits = 3),
             max_PM_yield = round(max(PM_y_treat, na.rm = TRUE),digits = 3),
             .groups = "drop")%>%
   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
   arrange(year)%>%
   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - ")) %>%
   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - ")) %>%
   mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield)) %>%
   flextable() %>%
   set_header_labels(trial_ref = "Trial code",
                     location = "Location",
                     year = "Year",
                     planting_date = "Sowing date",
                     first_sign_disease = "PM onset",
                     n = "n",
                     m_PM_sev_control = "Control median\nPM severity",
                     n_controls = "n controls",
                     PM_sev_range = "PM severity\nrange*",
                     m_PM_yield_control = "Control\nmean yield",
                     yield_range = "Yield range\n(t / ha)*"
                     ) %>%
   fontsize(size = 8,part = "body")%>%
   fontsize(size = 10, part = "header")%>%
   align(j = 3:10, align = "center", part = "all") %>%
   autofit() %>%
   width(j = 7:10, width = 0.9)%>%
   width(j = 3, width = 0.5)%>%
   set_caption("Table 1: Mean yield and severity for trials included in the meta-analysis. Powdery mildew (PM) onset, number of treatments per trial (n), PM mean plot severity of the non-fungicide treated plots and the severity range in fungicide treatments; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare")
Sev_yield_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = Sev_yield_table)
doc <- officer::body_end_section_landscape(doc)
print(doc, target = "paper/figures/Table1_severity&yield.docx")

@@

```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
PM_MB_dat %>%
   mutate(fungicide_ai = as.factor(PM_MB_dat$fungicide_ai)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl"
   ) %>%
   mutate(fungicide_ai = factor(
      fungicide_ai,
      levels = c(
         "carbendazim",
         "pyraclostrobin",
         "sulphur",
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "200 g/L tebuconazole + 120 g/L azoxystrobin"
      )
   )) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide_ai)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\nfaceted by number of sprays") +
   theme(legend.position = "none") +
   scale_fill_usq() +
   coord_flip()
```

@@

```{r PropiDoseEffect}
PM_MB_dat %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ylab("Yield gain proportially\nto the no spray control") +
   facet_grid(cols = vars(total_fungicide))
```

@@

```{r spray_relative2FS}
PM_MB_dat %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>%
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(labels = c(
      "First spray",
      "Second spray",
      "Third spray",
      "Fourth spray",
      "Fifth spray"
   )) +
   ylab("Number of days after or before first sign of powdery mildew") +
   ggtitle("Fungicide application timing relative to First Sign of Disease.\n - Faceted by number of applications")+
   facet_grid(cols = vars(total_fungicide)) +
   coord_flip()
```

@@

Lets plot disease severity in boxplots grouped by row spacing treatment.
We are asking here, which row spacing leads to the higher disease severity?

@@

There is little difference here between the row spacing treatments, lets look if there is a trial location effect as disease pressure lead to varying results.

@@

Mungbean Jade shows the best quantitative resistance to powdery mildew.
Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.
```{r JadeYieldLoss}
PM_MB_dat %>%
   filter(year == "2016",
          host_genotype == "Jade")%>%
   mutate(Treatment = case_when(
      fungicide_ai == "control" ~ "control",
      TRUE ~ "FungicideTreated"))%>%
   group_by(location, Treatment)%>%
   summarise(trial_ref = trial_ref,
             location = location, 
             year = year,
             Yield = mean(grain_yield.t.ha., na.rm = TRUE),
             .groups = "drop")%>%
   distinct()%>%
   pivot_wider(names_from = Treatment, values_from = Yield)%>%
   mutate(Diff = FungicideTreated - control) %>%
   mutate(percent = (Diff/FungicideTreated)*100)%>%
   select(trial_ref, location, year, control, FungicideTreated,percent, Diff)

@@

An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
Lets pull in data from the FAOSTAT website for the area of mungbean crops harvested.

@@

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested")%>%
   select(Year,Value)%>%
   ggplot(aes(y = Value, x = Year))+
   geom_point()+
   geom_smooth()

>>>>

All fungicide AI treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.

@@

Let's look at how many trials were undertaken each season in trials including DMI fungicides.

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref, location, year) %>%
   arrange(year)
table(tmp1$year)
```

@@

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_SE = sd(grain_yield.t.ha. * 1000) /
         sqrt(n())
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for no spray control plots")
```

What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
```{r ControlYield_DMITrials}
DMITrials <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   distinct(trial_ref) %>%
   pull()

PM_MB_dat %>%
   filter(trial_ref %in% DMITrials) %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_sterr = sd(grain_yield.t.ha. * 1000) / (sqrt(length(grain_yield.t.ha.)))
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for control plots in trials which used a DMI fungicide")
```

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

@@

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

@@

Let's look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.

```{r Calculate_yield-savings}
for (i in unique(PM_MB_dat$trial_ref)) {
   # Loop code over each trial reference
   dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == i,]

@@

   for (j in unique(dat1$row_spacing)) {
      # Loop within trial row_spacing
      dat2 <- dat1[dat1$row_spacing == j,]
      controlY <-
         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."]) #Mean taken as some trials had multiple control reps

@@

      # Reassign values to row_spacing subset
      dat1[dat1$row_spacing == j,] <- dat2
   }
   # Reassign values to trial_ref subset
   PM_MB_dat[PM_MB_dat$trial_ref == i,] <- dat1
}

# ____________________________________________
# calculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",]

@@

PM_MB_dat[PM_MB_dat$trial_ref == "AM1303",] <- dat1
```

Let's show the yield gains in each trial as a table and plot
```{r YieldGain_table}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   group_by(trial_ref, location, year)%>%
   summarise(yield_gain_m = mean(yield_gain),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             yg_n = n(),
             .groups = "drop")%>%
   arrange(yield_gain_m)
```

```{r Yield_plot}
bw_labels <-
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials) %>%
   group_by(trial_ref, location, year) %>%
   summarise(m_gy = mean(grain_yield.t.ha.)) %>%
   mutate(trial = paste(location, year, sep = "\n")) %>%
   arrange(m_gy) %>%
   pull(trial)

bw_labels[1] <- paste0(bw_labels[1], "(b)")
bw_labels[3] <- paste0(bw_labels[3], "(a)")

fungicide_spray_plot <-
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials) %>%
   mutate(spray_treat = ifelse(fungicide_ai == "control", "control", "Fungicide treated")) %>%
   group_by(trial_ref, location, year) %>%
   ggplot(aes(
      reorder(trial_ref, grain_yield.t.ha.),
      grain_yield.t.ha.,
      fill = spray_treat
   )) +
   geom_boxplot() +
   theme(axis.text.x = element_text(
      angle = 90,
      hjust = 1,
      vjust = 0.3
   )) +
   xlab("Trial location and year") +
   ylab(bquote('Mungbean yield  ' * t ~ ha ^ -1 * '')) +
   scale_x_discrete(labels = bw_labels) +
   ylim(0, 2.5) +
   scale_fill_grey(start = 1, end = 0.7) +
   labs(colour = "Fungicide treatment") +
   guides(fill = guide_legend(title = "Treatment"))

@@

Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.

```{r Full_Trial_Summary_table, warning= FALSE}
Sev_yield_table <-
   PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                   TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                   TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                 TRUE ~ NA_real_)) %>%
   mutate(trial_ref = str_remove(trial_ref, "mung")) %>%  # remove "mung" prefix from trial_ref
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(
      n = n(),
      m_PM_sev_control = round(median(PM_sev_control, na.rm = TRUE), digits = 2),
      n_controls = sum(is.na(PM_sev_control) == FALSE),
      min_PM_sev = round(min(PM_sev_treat, na.rm = TRUE), digits = 2),
      max_PM_sev = round(max(PM_sev_treat, na.rm = TRUE), digits = 2),
      m_PM_yield_control = round(mean(PM_y_control, na.rm = TRUE), digits = 3),
      min_PM_yield = round(min(PM_y_treat, na.rm = TRUE), digits = 3),
      max_PM_yield = round(max(PM_y_treat, na.rm = TRUE), digits = 3),
      .groups = "drop"
   ) %>%
   filter(min_PM_sev < 10) %>% # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
   arrange(year) %>%
   mutate(PM_sev_range = paste(min_PM_sev, max_PM_sev, sep = " - ")) %>%
   mutate(yield_range = paste(min_PM_yield, max_PM_yield, sep = " - ")) %>%
   mutate(m_PM_sev_control = paste(m_PM_sev_control, " (", n_controls, ")", sep = "")) %>%
   select(-c(min_PM_sev, max_PM_sev, min_PM_yield, max_PM_yield, n_controls)) %>%
   select(c(1:7, 9, 8, 10)) %>% # order columns
   flextable() %>%
   set_header_labels(
      trial_ref = "Trial code",
      location = "Location",
      year = "Year",
      planting_date = "Sowing date",
      first_sign_disease = "PM onset",
      n = "n",
      m_PM_sev_control = "Control median\nPM severity",
      PM_sev_range = "PM severity\nrange*",
      m_PM_yield_control = "Control\nmean yield*",
      yield_range = "Yield range\n(t / ha)"
   ) %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   align(j = 3:10, align = "center", part = "all") %>%
   autofit() %>%
   width(j = 7:10, width = 1) %>%
   width(j = 3, width = 0.5) %>%
   set_caption(
      "Table 1: Mean yield and severity for trials included in the meta-analysis. Powdery mildew (PM) onset, number of treatments per trial (n), PM median plot severity of the non-fungicide treated plots and the severity range in fungicide treatments, * bracketed numbers refer to the number of pooled control treatments summarised; Mean yield in non-fungicide treated control and the range of yields in the fungicide treatments in tonnes per hectare"
   )
Sev_yield_table
```

```{r eval=FALSE, include=FALSE}
# Save table as a word document
doc <- officer::read_docx()
doc <- body_add_flextable(doc, value = Sev_yield_table)
doc <- officer::body_end_section_landscape(doc)
print(doc, target = "paper/figures/Table1_severity&yield.docx")
```

@@

```{r Fungicide_x_nSprays_tble1, message=FALSE, warning=FALSE}
PM_MB_dat %>%
   mutate(fungicide_ai = as.factor(PM_MB_dat$fungicide_ai)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl"
   ) %>%
   mutate(fungicide_ai = factor(
      fungicide_ai,
      levels = c(
         "carbendazim",
         "pyraclostrobin",
         "sulphur",
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "200 g/L tebuconazole + 120 g/L azoxystrobin"
      )
   )) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide_ai)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved",
        caption = "Facets indicate number of sprays") +
   theme(legend.position = "none") +
   scale_fill_usq() +
   coord_flip()
```

@@

```{r PropiDoseEffect}
PM_MB_dat %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   labs(label = "Yield for each respective propiconazole dose",
        caption = "Facets indicate the number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   ylab("Yield gain proportially\nto the no spray control") +
   facet_grid(cols = vars(total_fungicide))
```

@@

```{r spray_relative2FS}
PM_MB_dat %>%
   mutate(
      s1_DfromFS = fungicide_application_1 - first_sign_disease,
      s2_DfromFS = fungicide_application_2 - first_sign_disease,
      s3_DfromFS = fungicide_application_3 - first_sign_disease,
      s4_DfromFS = fungicide_application_4 - first_sign_disease,
      s5_DfromFS = fungicide_application_5 - first_sign_disease
   ) %>%
   gather(
      key = spray,
      value = n_days,
      s1_DfromFS,
      s2_DfromFS,
      s3_DfromFS,
      s4_DfromFS,
      s5_DfromFS
   ) %>%
   drop_na(n_days) %>%
   ggplot(aes(x = spray, y = as.numeric(n_days))) +
   geom_violin() +
   scale_x_discrete(labels = c(
      "First spray",
      "Second spray",
      "Third spray",
      "Fourth spray",
      "Fifth spray"
   )) +
   ylab("Number of days after or before first sign of powdery mildew") +
   labs(title = "Fungicide application timing relative to First Sign of Disease",
        caption = "Facets indicate the number of applications") +
   facet_grid(cols = vars(total_fungicide)) +
   coord_flip()
```

@@

Let's plot disease severity in boxplots grouped by row spacing treatment.
We are asking here, which row spacing leads to the higher disease severity?

@@

There is little difference here between the row spacing treatments, Let's look if there is a trial location effect as disease pressure lead to varying results.

@@

Mungbean Jade shows the best quantitative resistance to powdery mildew.
Based on a GRDC report by Sue Thompson [-@SueThompson2016] we want to know what the yield loss was in on cultivar Jade in the 2016 Trials.

```{r JadeYieldLoss}
PM_MB_dat %>%
   filter(year == "2016",
          host_genotype == "Jade") %>%
   mutate(Treatment = case_when(fungicide_ai == "control" ~ "control",
                                TRUE ~ "FungicideTreated")) %>%
   group_by(location, Treatment) %>%
   summarise(
      trial_ref = trial_ref,
      location = location,
      year = year,
      Yield = mean(grain_yield.t.ha., na.rm = TRUE),
      .groups = "drop"
   ) %>%
   distinct() %>%
   pivot_wider(names_from = Treatment, values_from = Yield) %>%
   mutate(Diff = FungicideTreated - control) %>%
   mutate(percent = (Diff / FungicideTreated) * 100) %>%
   select(trial_ref,
          location,
          year,
          control,
          FungicideTreated,
          percent,
          Diff)
```

## Summary of disease incidence effect on yields

@@

An important consideration for why to carry out work on mungbean diseases is the value the crop provides. 
Let's pull in data from the FAOSTAT website for the area of mungbean crops harvested.

@@

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested") %>%
   select(Year, Value) %>%
   ggplot(aes(y = Value, x = Year)) +
   geom_point() +
   geom_smooth()
```
